### 2023-03-30 resilience.tex
up

\alain{dessous: à dire mais pas sous forme de proposition}
\begin{proposition}[Reformulation]\label{reformulation}
$\mathscr{S}=(S,\rightarrow,\leq)$ is %uniformely 
(\Bad,\Safe)-resilient iff $\Bad \subseteq \pred^*(\Safe)$.\\
$\mathscr{S}=(S,\rightarrow,\leq)$ is %uniformely 
(\Bad,\Safe)-$k$-resilient iff $\Bad \subseteq \pred^k(\Safe)$.
\end{proposition}

@@

In \cite{DBLP:conf/gg/Ozkan22}, the authors considered that $\Bad$ is downward closed and $\Safe$ is upward closed.
%		
RP is decidable for lossy counter machines (LCM) with $\Safe$ and $\Bad$ semilinear sets as a consequence of results in Section 3.4 of \cite{DBLP:conf/rp/Schnoebelen10}. We deduce that the three resilience problems are decidable for all four pairs of sets $\Safe$ and $\Bad$ downward closed and upward closed sets.

>>>>

% \alain{dessous: à dire mais pas sous forme de proposition}
\begin{remark}[Reformulation]\label{reformulation}
$\mathscr{S}=(S,\rightarrow,\leq)$ is %uniformely 
(\Bad,\Safe)-resilient iff $\Bad \subseteq \pred^*(\Safe)$.\\
$\mathscr{S}=(S,\rightarrow,\leq)$ is %uniformely 
(\Bad,\Safe)-$k$-resilient iff $\Bad \subseteq \pred^{\leq k}(\Safe)$.
\end{remark}

@@

In \cite{DBLP:conf/gg/Ozkan22}, the authors considered that $\Bad$ is downward closed and $\Safe$ is upward closed.
%		
RP is decidable for lossy counter machines (LCM) with $\Safe$ and $\Bad$ semilinear sets as a consequence of results in Section 3.4 of \cite{DBLP:conf/rp/Schnoebelen10}. We deduce \textcolor{red}{that the three resilience problems are decidable for all four pairs of sets $\Safe$ and $\Bad$ downward closed and upward closed sets.}

\mathieu{changer ça}
